Supporting Information

### 2015-10-21 si.Rmd
Match expressed genes to DESeq2 coldata by library rather than for the whole table (fixes # 14)

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage{caption}
  \captionsetup[figure]{labelfont=bf}
  \renewcommand{\thefigure}{S\arabic{figure}}
output:
  rmarkdown::tufte_handout:
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    number_sections: yes
    dev: "CairoPDF"
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
#               fig.align = 'center', 
               dev = "cairo_pdf",
               dpi=300,
               fig.show='hold',
               fig.height = 3.150,
               fig.width = 3.150,
               out.width = 3.150,
               out.height = 3.150,
#               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

``` {r st_libStats, results = "asis", fig.cap = I(pasteLabel("**Table S", s_tableCount, "st_libStats"))}
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
  "**: Library and sequencing statistics."))
pander::pandoc.table(st_libStats, split.tables = Inf, missing = "", round = 1, emphasize.strong.cols = 1,
                     justify = c("right", rep("center", length(names(st_libStats)) - 1)))
```

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage{caption}
  \captionsetup[figure]{labelfont=bf}
  \renewcommand{\thefigure}{S\arabic{figure}}
output:
  rmarkdown::tufte_handout:
    dev: CairoPDF
  BiocStyle::html_document:
    dev: CairoPDF
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               fig.align = 'center', 
#               dev=c("png", "cairo_pdf"),
               dpi=300,
               fig.show='hold',
               fig.height = 3.150,
               fig.width = 3.150,
               out.width = 3.150,
               out.height = 3.150,
#               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

``` {r st_libStats, results = "asis", fig.fullwidth = TRUE, fig.cap = I(pasteLabel("**Table S", s_tableCount, "st_libStats"))}
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
  "**: Library and sequencing statistics."))
pander::pandoc.table(st_libStats,
                     missing = "",
                     round = 1,
                     emphasize.strong.cols = 1,
                     split.tables = Inf,
                     justify = c("right", rep("center", length(names(st_libStats)) - 1)))
```
